### 2015-07-07 paper.tex
optimize the part: Natural radioactivity estimation

		\section{The event rate estimation of central detector}
		The JUNO detector consists of a central detector, a water 
		cherenkov detector and a muon tracker.So we estimate the event
		rate of each part respectively.The central detector is the 
		main part of JUNO detector.As we mentioned previously, 
		the signal
		rate is about 40/day. We will discuss the background in the 
		following.

@@

>>>>

		\section{The event rate estimation of central detector}
		The JUNO detector consists of a central detector, a water 
		cherenkov detector and a muon tracker. The central detector is the 
		main part of JUNO detector.As we mentioned previously, 
		the signal
		rate is about 40/day. We will discuss the background in the 
		following.

@@

		You may notice that when the energy threshold set to 0.1MeV the singles rate turned very
		large. It's becasue the radioelement C14 in LS with very high radioactive activity and very
		few energy depositing in each event. We just assume the concentration of C14 in LS is $10^{-18}$ g/g
		to do this estimation.
